Numerical simulation of the Cordilleran ice sheet \\ through the last glacial cycle

### 2014-06-29 kappa.tex
Add figures in the introduction.

% Base class and packages
\documentclass{article}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno}
\usepackage{natbib}
\usepackage[onehalfspacing]{setspace}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
%\usepackage{graphicx}

@@

@@

\todo{Figure. Glacier crevasse photo}\\
\todo{Figure. Glacier flowing photo}\\
\todo{Figure. Glacier moraine photo}\\
\todo{Figure. Benthic oxygen isotopes stack}\\
\todo{Figure. Modern and former ice sheets}

>>>>

% Base class and packages
\documentclass{article}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{lineno}
\usepackage{natbib}
\usepackage[onehalfspacing]{setspace}
\usepackage{physics}
\usepackage[colorlinks, citecolor=blue]{hyperref}
\usepackage[sort]{cleveref}  % needs to be loaded after hyperref
\usepackage{graphicx}
\graphicspath{{figures/}}

@@

% Text label over graphics
% from http://tex.stackexchange.com/questions/128844/put-subfigure-labels-
% inside-figures-using-subfig-package
\newcommand{\subgraphics}[3][,]{%
  \setbox1=\hbox{\includegraphics[#1]{#3}}% Store image in box
  \leavevmode\rlap{\usebox1}% Print image
  \rlap{\hspace*{0.25em}
        \raisebox{\dimexpr\ht1-3ex}{\textbf{(#2)}}}% Print label
  \phantom{\usebox1}% Insert appropriate spacing
  \hspace{1cm}% Add horizontal separator
}

% Finally to not include graphics
%\renewcommand{\includegraphics}[2][,]{}
%\renewcommand{\subgraphics}[3][,]{}
%\usepackage{endfloat}
%\renewcommand{\efloatseparator}{\mbox{}}

@@

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics{a}{photo-glacier-crevasses}
    \subgraphics{b}{photo-glacier-fold}
  }
  \caption{Different mechanical behaviours of glacier ice.
           \textbf{(a)} Brittle behaviour. Ice flowing over a hidden bedrock
           knob, resulting in fracturing at the glacier surface.
           Glacier Blanc, French Alps.
           \textbf{(b)} Ductile behaviour. Mountain glacier calving into a
           small lake, revealing a folded structure formed by deformed rock
           layers in the ice.}
  \label{fig:glacier-mechanics}
\end{figure}

% Alternative code using subcaption package
%\usepackage{subcaption}
%\begin{figure}
%  \centering
%  \makebox[0pt]{
%    \begin{subfigure}[t]{80mm}
%        \includegraphics{photo-glacier-crevasses}
%        \caption{Subcaption a.}
%        \label{fig:1a}
%    \end{subfigure}
%    \hspace{10mm}
%    \begin{subfigure}[t]{80mm}
%        \includegraphics{photo-glacier-fold}
%        \caption{Subcaption b.}
%        \label{fig:1b}
%    \end{subfigure}
%  }
%  \caption{Global caption.}
%  \label{fig:1}
%\end{figure}

\begin{figure}
  \centering
  \makebox[0pt]{
    \subgraphics[width=50mm]{a}{photo-glacial-valley}
    \subgraphics[width=50mm]{b}{photo-erratic-boulder}
    \subgraphics[width=50mm]{c}{photo-melt-channels}
  }
  \caption{Different indicators of past glaciation.
           \textbf{(a)} Glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers.
           Cirque du Fer-\`{a}-Cheval, French Alps.
           \textbf{(b)} Erratic boulders, deposited in an improbable
           arrangement as the glacier melted underneath.
           Finse area, Norwegian Scandes.
           \textbf{(c)} Lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom. Tuya Lake
           area, Canadian Cordillera.}
  \label{fig:glaciation-indicators}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-timeseries}
  \caption{The oxygen isotope record from oceanic sediments is a proxy for ice
           volume on land during Earth's hitory. Over the last million years,
           it shows predominance of a 100\,ka cycle of glacial and
           interglacial periods. This thesis focuses on the last glacial cycle.
           \todo{This figure is directly from \citet{Lisiecki.Raymo.2005}.
           Redraw it using the data they provide.}}
  \label{fig:palaeo-timeseries}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=80mm]{paleo-glaciation}
  \caption{Spatial extent of the last glacial maximum northern hemisphere ice
           sheets, after \citep{Ehlers.Gibbard.2007}.
           \todo{Rotate by 90\degree, re-centre, and compare with present-day
           ice cover. Maybe label the major ice sheets: CIS, LIS, GIS, FIS...}}
  \label{fig:palaeo-glaciation}
\end{figure}
